---
title: "Feeding Liquid Interaction Counter(FLIC): One Choice"
author: "Kayla Audette"
date: "December 6, 2023"
output:
  html_document:
    css: styles.css
---

### 1. R Environment

- **Setting Up Environment:**
  - The first chunk configures the presentation options for the R code.
  - It hides the code and result outputs, such as messages and warnings.
  - The workspace is cleared to remove any existing variables or data.
  - Essential libraries are loaded for data analysis and visualization.
  
- **Loading Directory and Attachments**
  - The working directory is set to "~/Working Directory," where R will locate and save files.
  - The "FLICFunctions" data is attached, making its functions accessible for use.

```{r setup, results='hide', message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Clears workspace
rm(list=ls())

# Essential libraries
library(ggplot2)
library(stats)
library(reshape2)
library(tidyverse)
library(data.table)
library(english)
library(gtools)

# Sets the working directing and attaches the programmed FLICFunctions
setwd("~/Working Directory")
attach("FLICFunctions",pos=2)
```


### 2. Parameter Initialization and Exploration

- **Initialization of Single-Well Parameters:**
  - The code initiates a parameter set (`p.single`) using the `ParametersClass.SingleWell()` class, tailored for a single-well experimental configuration.
  - A vector (`monitors.single`) is defined, enumerating monitor IDs (`1, 2, 3, 4`).
  - Monitors are explicitly specified, and a list of parameter objects is generated, associating each monitor with the common parameter set `p.single`.

- **Exploration of Parameter Attributes:**
  - The script explores the attributes and parameters within the `p.single` object.
  - `attributes(p.single)` is used to reveal additional information about the parameter object.
  - The content of `p.single` is displayed, offering insights into threshold signals for licks, event durations, and other relevant parameters.
  
```{r, message=FALSE, warning=FALSE}
p.single <- ParametersClass.SingleWell()
monitors.single <- c(1,2,3,4)
attributes(p.single)
p.single
#p.choice<-SetParameter(p.choice,Feeding.Threshold=30) [example code if you want to alter any of the parameters]
```


### 3. Monitor Data Transformation

- **Transforming Raw Monitor Data:**
  - Raw monitor data is transformed for each monitor (`dfm.single1` to `dfm.single4`) using the `DFMClass` with specific parameters.
  - Four instances of the `DFMClass` are created, each associated with a distinct monitor (1 to 4), utilizing the parameter set `p.single`.
  - This step involves the processing and organization of raw monitor data, preparing it for subsequent analysis.
  
```{r, results='hide', message=FALSE, warning=FALSE}
# Reads and transforms the parameter monitor data into the actually intended variable based on what was chosen (i.e licks, events, event duration etc.)
dfm.single1 <- DFMClass(1, p.single)
dfm.single2 <- DFMClass(2, p.single)
dfm.single3 <- DFMClass(3, p.single)
dfm.single4 <- DFMClass(4, p.single)
```

 
### 4. Summary Table Creation

- **Initializing List for Summary Tables:**
  - An empty list (`summary_tables`) is initialized to store summary tables, providing an organized structure for the analysis results.

- **Iterating Through Monitors:**
  - A loop iterates through monitors (1 to 4), creating summary tables using the `Feeding.Summary.DFM` function.
  - Summary tables are based on the transformed monitor data, and each table corresponds to a specific monitor.

- **Storing Summary Tables:**
  - The generated summary tables are stored in the `summary_tables` list, facilitating further examination or utilization.
  
```{r, results='hide', message=FALSE, warning=FALSE}
# Initialize a list to store summary tables
summary_tables <- list()

# Loop through monitors and create summary tables
for (i in 1:4) {
  dfm_single <- get(paste0("dfm.single", i))
  summary_tables[[i]] <- Feeding.Summary.DFM(dfm_single, range = c(5, 180), TransformLicks = FALSE)
}
```


### 5. Table Processing

- **Extracting Summary Tables**
  - Extraction of summary tables for each monitor from the summary_tables list.
  - Assignment of each summary table to individual variables (DFM1_summary to DFM4_summary).
 
```{r, results='hide', message=FALSE, warning=FALSE}
# Takes the summary table for the first monitor (Monitor One) from the summary_tables list and assigns it to a new variable named DFM1_summary.
DFM1_summary <- summary_tables[[1]]
DFM2_summary <- summary_tables[[2]]
DFM3_summary <- summary_tables[[3]]
DFM4_summary <- summary_tables[[4]]
```


### 6. Table Transformation

- **Function Definition:** 
  - The function `process_monitor_summary` is defined to process the summary of each monitor individually.
  - It selects specific columns, such as "DFM," "Chamber," "Licks," "Events," and "MeanDuration."
  - The factor variable "Chamber" is transformed using the `english` function and renamed as "Genotype" using the `recode_factor` function.
  - The processed summary is returned.

- **Processing Each Monitor:**
  - The `process_monitor_summary` function is called for each monitor (`DFM1_summary` to `DFM4_summary`).
  - Each monitor's summary is processed individually.

```{r}
# Function to Process Monitor Summary
process_monitor_summary <- function(DFM_summary, monitor_name) {
  # Select the desired columns
  DFM_summary <- DFM_summary[c("DFM", "Chamber", "Licks", "Events", "MeanDuration")]
 
  DFM_summary$Chamber <- as.character(english(DFM_summary$Chamber))
  DFM_summary$Genotype <- recode_factor(DFM_summary$Chamber, one = "genotype", two = "genotype", three = "genotype", four = "genotype", five = "genotype", six = "genotype", seven = "genotype", eight = "genotype", nine = "genotype", ten = "genotype", eleven = "genotype", twelve = "genotype")

# Code to write separate monitors data tables
  # Write the summary to a CSV file
  # file_name <- paste(monitor_name, "SummaryCondensed.csv", sep = "")
  # write.csv(DFM_summary, file_name, row.names = FALSE)
  
  return(DFM_summary)
}

# Process each monitor's summary individually
DFM1_summary <- process_monitor_summary(DFM1_summary, "DFM1")
DFM2_summary <- process_monitor_summary(DFM2_summary, "DFM2")
DFM3_summary <- process_monitor_summary(DFM3_summary, "DFM3")
DFM4_summary <- process_monitor_summary(DFM4_summary, "DFM4")
```


### 7. Table Combination and Export

- **Combined Results Data Frame:**
  - An empty data frame (`combined_results`) is created to store the combined results.

- **Appending Results:**
  - The processed summaries for each monitor are appended to the `combined_results` data frame using `rbind`.

- **Exporting Combined Results:**
  - The combined results are written to a CSV file named "All_Monitors_Results.csv" using the `write.csv` function.
  - The CSV file does not include row names.

```{r}
# Create an empty data frame to store the combined results
combined_results <- data.frame()

# Append the results to the combined data frame
combined_results <- rbind(combined_results, DFM1_summary, DFM2_summary, DFM3_summary, DFM4_summary)

# Write the combined results to a CSV file
write.csv(combined_results, "All_Monitors_Results.csv", row.names = FALSE)
```

   
   
   
   
   