---
title: "Simple FLIC Output"
author: "Kayla Audette"
date: "2023-11-06"
output: html_document
---

### 1. R Environment

- **Setting Up Environment:**
  - The first chunk configures the presentation options for the R code.
  - It hides the code and result outputs, such as messages and warnings.
  - The workspace is cleared to remove any existing variables or data.
  - Essential libraries are loaded for data analysis and visualization.
  
- **Loading Directory and Attachments**
  - The working directory is set to "~/Working Directory," where R will locate and save files.
  - The ".FLICFunctions" data is attached, making its functions accessible for use.
  
```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())

library(dplyr)
library(readr)
library(tidyr)

setwd("~/Working Directory")
```


### 2. Data Processing

- **Defining Data Frame:**
  - This chunk is responsible for processing data from multiple CSV files.
  - Creates an empty data frame `combined_results` to store the final results.
  - Defines a list of CSV file names (`file_names`) to be processed.
  - Iterates through each file, reading it into a data frame (`data`).
  
- **Constructing Data Frame**
  - Analyzes 12 variables in each file, calculating counts above 20, first and last numbers for each variable.
  - Constructs a data frame (`file_results`) for each file and appends it to the `combined_results`.
  
```{r, results='hide', message=FALSE, warning=FALSE}
# Create an empty data frame to store the results
combined_results <- data.frame()

# List of CSV file names
file_names <- c("DFM1_0.csv", "DFM2_0.csv", "DFM3_0.csv", "DFM4_0.csv")  # Add the names of your CSV files

# Iterate through the list of file names
for (file_name in file_names) {
  # Read the CSV file into a data frame
  data <- read.csv(file_name)
  
  # Create a list to store results for all 12 variables
  results_list <- lapply(1:12, function(i) {
    variable_name <- paste0("W", i)
    column_to_analyze <- data[, variable_name]
    count_above_20 <- sum(column_to_analyze > 20)
    first_number <- column_to_analyze[1]
    last_number <- column_to_analyze[length(column_to_analyze)]
    data.frame(
      File = file_name,  # Add a column to track the source file
      Variable = variable_name,
      CountAbove20 = count_above_20,
      FirstNumber = first_number,
      LastNumber = last_number
    )
  })

  # Combine the results into a single data frame for this file
  file_results <- do.call(rbind, results_list)
  
  # Append the results for this file to the combined_results data frame
  combined_results <- rbind(combined_results, file_results)
}
```


### 3. Results Display

- **Exporting Results:**
  - This chunk is responsible for displaying and saving the final results.
  - Prints the `combined_results` data frame to the console.
  - Saves the `combined_results` data frame to a CSV file named "Simple_Output.csv".
  
```{r, results='hide', message=FALSE, warning=FALSE}
# Print the combined results
print(combined_results)

# Save the combined results to a single CSV file
write.csv(combined_results, "Simple_Output.csv", row.names = FALSE)
```
