---
title: "Feeding Liquid Interaction Counter(FLIC): Two-Choice"
author: "Kayla Audette"
date: "December 6, 2023"
output:
  html_document:
    css: styles.css
---

### 1. R Environment

- **Setting Up Environment:**
  - The first chunk configures the presentation options for the R code.
  - It hides the code and result outputs, such as messages and warnings.
  - The workspace is cleared to remove any existing variables or data.
  - Essential libraries are loaded for data analysis and visualization.
  
- **Loading Directory and Attachments**
  - The working directory is set to "~/Working Directory," where R will locate and save files.
  - The "FLICFunctions" data is attached, making its functions accessible for use.

```{r setup, results='hide', message=FALSE, warning=FALSE}
# Set up options for the R code
knitr::opts_chunk$set(echo = TRUE)

# Clear the workspace
rm(list=ls())

# Load necessary libraries
library(ggplot2)
library(stats)
library(gridExtra)
library(reshape2)
library(gtools)
library(dplyr)
library(tidyverse)

# Set the working directory
setwd("~/Working Directory")

# Attach the "FLICFunctions" data; assuming it's a global environment object
attach("FLICFunctions", pos = 2)
```


### 2. Initializing and Displaying Parameters

- **Initializing Parameters:**
  - Initialization of a parameter set (`p.choice`) using the `ParametersClass.TwoWell()` class.
  - The `ParametersClass.TwoWell()` function is employed to define a set of parameters relevant to a two-well experimental setup.

- **Displaying Parameters:**
  - Attributes and parameters within the `p.choice` object are displayed.
  - The code utilizes `attributes(p.choice)` to provide additional information about the object.
  - The content of `p.choice` is printed to the console, revealing details such as threshold signal for a lick, duration of an event, etc.
   
```{r, message=FALSE, warning=FALSE}
 # Creates a data set with parameters for the data (e.g., threshold signal for a lick, duration of an event, etc.)
p.choice <- ParametersClass.TwoWell()
attributes(p.choice)
p.choice
```


### 3. Applying Parameters to Data

- **Parameter Initialization:**
  - Two instances of `ParametersClass.TwoWell()` are created and assigned to `p.choice.one` and `p.choice.two`, defining parameters for a two-well experimental setup.

- **Adjusting `p.choice.two`:**
  - The `SetParameter()` function modifies parameters for `p.choice.two`, specifically setting `PI.Multiplier` to 1.0.
  - This adjustment suggests customization for a specific condition or scenario.

- **Monitor Selection:**
  - A vector, `monitors.choice`, is created with values 1, 2, 3, and 4.
  - These values likely represent the chosen monitors or data sources for processing with corresponding parameter sets.

- **List of Parameter Objects:**
  - A list, `p.choice.list`, is constructed with elements `p.choice.two`, `p.choice.one`, `p.choice.two`, and `p.choice.one`.
  - This list associates specific parameter sets with monitors for subsequent analysis.

```{r,  results='hide', message=FALSE, warning=FALSE}
# Applies parameters to the raw monitor output data 
p.choice.one <- ParametersClass.TwoWell()
p.choice.two <- ParametersClass.TwoWell()
p.choice.two <- SetParameter(p.choice.two, PI.Multiplier = 1.0)
monitors.choice <- c(1, 2, 3, 4)
p.choice.list <- list(p.choice.two, p.choice.one, p.choice.two, p.choice.one)
```


### 4. Creating DFM Objects:

- **Creating DFM Objects:**
   - Four instances of the `DFMClass` are created and assigned to `dfm_own1`, `dfm_own2`, `dfm_own3`, and `dfm_own4`.
   - Each instance is associated with a specific monitor (1, 2, 3, or 4), and the same parameter set `p.choice` is passed to each instance.

- **Initialization of DFM Instances:**
   - The `DFMClass` is presumably a custom function used to define and initialize data frame monitors. It takes two arguments: the monitor number and the parameter set (`p.choice`).
   - Each `DFMClass` instance is associated with a specific monitor number (1, 2, 3, or 4) and the common parameter set `p.choice`.

```{r,  results='hide', message=FALSE, warning=FALSE}
# Reads and transforms the parameter monitor data into the intended variable based on the chosen parameters
dfm_own1 <- DFMClass(1, p.choice)
dfm_own2 <- DFMClass(2, p.choice)
dfm_own3 <- DFMClass(3, p.choice)
dfm_own4 <- DFMClass(4, p.choice)
```


### 5. Combining Monitor Summaries and Exporting

- **Combining Summary Tables:**
  - A list, `FeedingSummary`, is created to store summary tables for each monitor.
  - A loop reads raw data from monitor files and generates summary tables using the `Feeding.Summary.Monitors` function.
  - Each summary table is stored in the `FeedingSummary` list.

- **Processing Each Monitor Summary:**
  - A function, `process_monitor_summary`, is defined to select specific columns and add a "Genotype" column based on the "Chamber" variable.
  - The function is applied to each monitor's summary, creating processed summaries.

- **Combining Processed Summaries:**
  - The processed summaries for each monitor are combined into a single data frame, `combined_results`, using the `do.call(rbind, processed_summaries)` approach.

- **Exporting Combined Results:**
  - The combined results are written to a CSV file named "All_Monitors_Results.csv" using the `write.csv` function.
  - The CSV file does not include row names.
  
```{r, results='hide', message=FALSE, warning=FALSE}
# Initialize a list to store summary tables
FeedingSummary <- list()

# Loop through monitors and create summary tables
for (i in 1:1) {
  dfm.own <- get(paste0("dfm_own", i))
  FeedingSummary[[i]] <- Feeding.Summary.Monitors(monitors.choice, p.choice.list, range=c(5,180), TransformLicks=FALSE)
}

# Function to Process Monitor Summary
process_monitor_summary <- function(FeedingSummary, monitor_name) {
  # Check if FeedingSummary is a list; if not, return an empty data frame
  if (!is.list(FeedingSummary)) {
    return(data.frame())
  }

  # Check if FeedingSummary[[1]] is a data frame; if not, return an empty data frame
  if (!is.data.frame(FeedingSummary[[1]])) {
    return(data.frame())
  }

  # Select the desired columns
  processed_summary <- FeedingSummary[[1]][, c("DFM", "Chamber", "PI", "LicksA", "LicksB", "EventsA", "EventsB", "MeanDurationA", "MeanDurationB")]
  
  # Add the Genotype column
  processed_summary$Genotype = ifelse(processed_summary$Chamber %% 2 == 1, "Odds", "Evens")

  return(processed_summary)
}

# Process each monitor's summary individually
processed_summaries <- lapply(FeedingSummary, process_monitor_summary)

# Create an empty data frame to store the combined results
combined_results <- data.frame()

# Append the processed results to the combined data frame
combined_results <- do.call(rbind, processed_summaries)

# Write the combined results to a CSV file
write.csv(combined_results, "All_Monitors_Results.csv", row.names = FALSE)

```

